GlobalSearchRegression.jl \\ \vspace{5mm} REPORT

### 2019-07-26 src/Output/decorations/latex/tpl.tex
Intelligent text

%In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria. For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate. Available statistics suggests that there {{are or is}} {{numofpositivegainsvariables}} explanatory {{variable or variables}} that improved model accuracy. {{Among them, {{bestvar}} or {{bestvar}}}} helps to increase up to a {{gainsinperc}}\% the user selected information criteria. On the contrary, there {{are or is}} {{numofnegativegainsvariables}} {{covariate or covariates}} that have a deleterious impact on model accuracy. This is specially true for {{worstvar}}, which seems to decrease up to a {{lossinperc}}\% the user selected information criteria}}
{{/allsubsetregression}}

>>>>

{{#intelligent_text}}
In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria. For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate. Available statistics suggests that there {{^multiple_positive_variables}}is{{/multiple_positive_variables}}{{#multiple_positive_variables}}are{{/multiple_positive_variables}} {{numofpositivegainsvariables}} explanatory {{^multiple_positive_variables}}variable{{/multiple_positive_variables}}{{#multiple_positive_variables}}variables{{/multiple_positive_variables}} that improved model accuracy. {{#multiple_positive_variables}}Among them, {{/multiple_positive_variables}} {{ bestvar }} helps to increase up to a {{bestvar_gainsinperc}}\% the user selected information criteria. {{#no_negative_variables}}And least important variable is {{ worstvar }} which only increases information criteria in {{worstvar_gainsinperc}}\%.{{/no_negative_variables}}

{{^no_negative_variables}}On the contrary, there {{^multiple_negative_variables}}is{{/multiple_negative_variables}}{{#multiple_negative_variables}}are{{/multiple_negative_variables}} {{numofnegativegainsvariables}} {{^multiple_negative_variables}}covariate{{/multiple_negative_variables}}{{#multiple_negative_variables}}covariates{{/multiple_negative_variables}} that decreased the model accuracy. This is specially true for {{worstvar}}, which seems to decrease up to a {{worstvar_gainsinperc}}\% the user selected information criteria.{{/no_negative_variables}}
{{/intelligent_text}}

{{/allsubsetregression}}
